Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Address heap

We adopt a strong threat model in which both caller and callee may execute
arbitrary machine code. Hardware and timing attacks are out of scope.

\bcp{We should say explicitly that we do not address attacks on the heap
  (cite Arthur's paper and say we believe it can be combined smoothly with
  this), direct attacks on code (we assume that code can't be over written),
etc.}

>>>>

We adopt a strong threat model in which both caller and callee may execute
arbitrary machine code. Hardware and timing attacks are out of scope.
So are attacks on the heap -- we believe that the work of
\citet{DBLP:conf/post/AmorimHP18} can be combined smoothly with our
to protect both stack and heap.
